$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-05 paper/paper.tex
small updates to contexts

\begin{nidefinition}[Types and length-indexed typing contexts]
  \emph{Types} are defined in \autoref{fig:prectx} as either unit types (rule $\unit$), base types (rule $\base{n}$) or channel types (rule $\channel{t}{x}$).

  We keep track of types in a \emph{length-indexed typing context} $\PreCtx_n$, defined by the last row of rules in \autoref{fig:prectx}.
  A typing context is either empty $[]$ or the result of appending a type $t$ to an existing context$\gamma$.
  \begin{figure}[h]
  \begin{mathpar}
    \datatype
    { }
    {\Type : \Set}
    \; \textsc{Type}

@@

Notice that our notation of channel types is similar to Kobayashi's $[t]\mathbf{chan}_{(i^{y},o^{z})}$, where $y,z$ are the multiplicities of input and output \cite{K07}.

>>>>

\begin{nidefinition}[Types and length-indexed typing contexts]
  A \emph{Type} is either a unit type ($\unit$), a base type ($\base{n}$) or a channel type ($\channel{t}{x}$) defined in \autoref{fig:prectx}.

  A \emph{length-indexed typing context} $\PreCtx_n$, is defined by the last row of rules in \autoref{fig:prectx}.
  A typing context is either empty $[]$ or the result of appending a type $t$ to an existing context$\gamma$.
  \begin{figure}[h]
  \begin{mathpar}
    \datatype
    { }
    {\Type : \Set}
    \; \textsc{Type}

@@

Notice that our notation of channel types is similar to Kobayashi's $[t]\mathbf{chan}_{(i^{y},o^{z})}$, where $y,z$ are the multiplicities of input and output, respectively \cite{K07}.
